---
title: "workout01-leonard-yang"
output: github_document
---
```{r}
library(readr) #importing data
library(dplyr) #data wrangling
library(ggplot2) #graphics)
```

```{r}
nba = read_csv('/Users/leoyang19/desktop/hw-stat133/workout1/data/nba2018.csv')

nba$experience[nba$experience == "R"]<- 0
nba$experience=as.integer(nba$experience)
nba$salary <- nba$salary/1000000

nba$position <- nba$position <- factor(
  nba$position, labels = c("center", "power_fwd", "point_guard", "small_fwd", "shoot_guard"))

nba = mutate(nba, missed_ft = nba$points1_atts - nba$points1, 
                   missed_fg = nba$field_goals_atts - nba$field_goals, 
                   rebounds = nba$off_rebounds + nba$def_rebounds)

nba = mutate(nba, efficiency = ((nba$points + rebounds + nba$assists + nba$steals + nba$blocks
                                 - missed_fg - missed_ft - nba$turnovers) / nba$games))
```

```{r}
teams=data.frame(summarise(group_by(nba,team), 
                           experience=sum(experience), 
                           salary= round(sum(salary),2),
                           points3=sum(points3),
                           points2=sum(points2),
                           points1=sum(points1),
                           points=sum(points),
                           off_rebounds=sum(off_rebounds),
                           def_rebounds=sum(def_rebounds),
                           assists=sum(assists),
                           steals=sum(steals),
                           blocks=sum(blocks),
                           turnovers=sum(turnovers),
                           fouls=sum(fouls),
                           efficiency=sum(efficiency)
))
```


# 5) Ranking of Teams
```{r}
team_desc_salary= arrange(teams, desc(salary))
team_desc_salary
```

```{r}
ggplot(team_desc_salary, aes(x=reorder(team, salary), y=salary)) + 
  geom_hline(yintercept = mean(team_desc_salary$salary), color = "red") + 
  geom_bar(stat='identity') + labs(x='Team', y='Salary (in Millions)',
                                   title= 'NBA Teams ranked by Total Salary')+
  coord_flip()
```
```{r}
ggplot(team_desc_salary, aes(x=reorder(team, points), y=points)) +
  geom_hline(yintercept = mean(team_desc_salary$points), color = "red") + 
  geom_bar(stat='identity') + labs(x='Team', y='Points',
                                   title= 'NBA Teams ranked by Total Points')+
  coord_flip()
```
```{r}
ggplot(team_desc_salary, aes(x=reorder(team, efficiency), y=efficiency)) +
  geom_hline(yintercept = mean(team_desc_salary$efficiency), color = "red")+
  geom_bar(stat='identity') + labs(x='Team', y='Efficiency',
                                   title= 'NBA Teams ranked by Total Efficiency')+
  coord_flip()
```
#Own Index Barchart
```{r}
teams_assist_to=mutate(teams, assist_to = (teams$assists/teams$turnovers))
teams_assist_to
```

```{r}
ggplot(teams_assist_to, aes(x=reorder(team, assist_to), y=assist_to)) +
  geom_hline(yintercept = mean(teams_assist_to$assist_to), color = "red")+
  geom_bar(stat='identity') + labs(x='Team', y='Assists to Turnover Ratio',
                                   title= 'NBA Teams ranked by Total Assists to Turnover Ratio')+
  coord_flip()
```
- I used the assist to turnover ratio as my index, because this stat shows how well a team can control the ball and make as little mistakes as possible. The higher the assist to turnover ratio, the more assists a team has per turnover committed, which they move the ball around a lot better as a team, which leads to more scoring opportunities. 

#Comments and Reflections

• Was this your first time working on a project with such file structure? If yes, how do
you feel about it?
- No, I think we covered most of the file structures necessary in this project during labs.

• Was this your first time using relative paths? If yes, can you tell why they are important
for reproducibility purposes?
- No, we used them during lab. 

• Was this your first time using an R script? If yes, what do you think about just writing
code (without markdown syntax)?
- No, we also used them during lab. It is quicker but I like writing code on Rmd files because we get to clearly see what we are running. 

• What things were hard, even though you saw them in class/lab?
- making a dataframe was challenging and a little time consuming if the concepts are not clear. 

• What was easy(-ish) even though we haven’t done it in class/lab?
- Filtering and arranging data frames were easy, although we did cover in lab.

• Did anyone help you completing the assignment? If so, who?
- No. 

• How much time did it take to complete this HW?
- About 4 hours. 

• What was the most time consuming part?
- Writing the Data Dictionary and making a new teams dataframe. 

• Was there anything interesting?
- Analyzing data and making barcharts to see the distributions of salary, efficiency, and your own index (assist to turnover ratio for myself), was interesting. You could see that the good teams were usually the ones on top with the most frequencies. 